---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
unzip("activity.zip")  ##Unzip file
data <- read.csv("activity.csv") ##Load csv data
library(lubridate)
data$date <- ymd(data$date)      ##Convert to Date object
```



## What is mean total number of steps taken per day?
```{r}
stepsperday <- aggregate(steps~date,data=data,sum) ##Summarize steps by day
library(ggplot2)
qplot(stepsperday$steps,geom="histogram",binwidth=5000, main="Steps per Day", xlab="Steps", ylab="Frecuency")  ##Plot histogram
smean <- mean(stepsperday$steps)  ##Calculate values
smedian <- median(stepsperday$steps)
```

About the number of steps per day, the mean is `r as.integer(smean)` and the median is
`r smedian`.


## What is the average daily activity pattern?
```{r}
timeseries <- aggregate(steps ~ interval, data=data, mean) ##Calculate mean of steps by interval
with(timeseries,qplot(x=interval,y=steps,geom="line",xlab="Interval",
                      ylab="Steps",main="Steps by 5 minute intervals"))
##Plot
maxint <- with(timeseries,interval[steps==max(steps)])  ##Search interval with max steps count

```
The interval with max number of steps in the day is `r maxint`.


## Imputing missing values
```{r}
nincomplete <- sum(!complete.cases(data))
```
Number of incomplete rows: `r nincomplete`.

For imputing missing values, impute the mean value for steps by same intervals.
```{r}
impute <- function(df){
  for(i in seq(1,nrow(df))){
    if(is.na(df[i,1])){
      df[i,1] <- timeseries$steps[timeseries$interval==df[i,3]]
    }
  }
  df
}

idata <- impute(data)
```

Plot histogram...
```{r}
istepsperday <- aggregate(steps~date,data=idata,sum)
qplot(istepsperday$steps,geom="histogram",binwidth=5000, main="Steps per Day (Imputed NA's)", xlab="Steps", ylab="Frecuency")
ismean <- mean(istepsperday$steps)
ismedian <- median(istepsperday$steps)
```
About the number of steps per day, now with imputed values, the mean is `r as.integer(ismean)` and the median is
`r as.integer(ismedian)`. The shape of the histogram is the same, but the values era bit higher.

## Are there differences in activity patterns between weekdays and weekends?
```{r}
library(dplyr)
library(lattice)
idata <- mutate(idata,weekday=weekdays(idata$date))
idata <- mutate(idata,Temp = factor(idata$weekday,labels=c("Weekend","Week","Week","Week","Week","Weekend","Week")))
idata <- aggregate(steps ~ interval+Temp, data=idata, mean)
with(idata,xyplot(steps~interval |Temp,type="l",main="Average steps by interval on Week or Weekend days",ylab="Steps",xlab="Interval"))

```

